### 2009-07-09 docs/architecture/architecture.tex
a figure that shows boxes on a single level and the integer indices
reference figure

A \boxtype\ is simply a rectangular domain in space.  The datatype for
a \boxtype\ is
\begin{verbatim}
  type box
     integer :: dim  = 0
     integer :: lo(MAX_SPACEDIM) =  Huge(1)
     integer :: hi(MAX_SPACEDIM) = -Huge(1)
  end type box
\end{verbatim}

@@

Note that boxes do not hold the state data themselves.

add description of index-space

>>>>

A \boxtype\ is simply a rectangular domain in space.  Note that boxes
do not hold the state data themselves.  The datatype for a
\boxtype\ is
\begin{verbatim}
  type box
     integer :: dim  = 0
     integer :: lo(MAX_SPACEDIM) =  Huge(1)
     integer :: hi(MAX_SPACEDIM) = -Huge(1)
  end type box
\end{verbatim}

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption{\label{fig:boxes} Three boxes that comprise a single level.
At this resolution, the domain is 20$\times$18 zones.}
\end{figure}

The computational domain is divided into boxes.  The collection of
boxes with the same resolution comprise a level.
Figure~\ref{fig:boxes} shows three boxes in the same level of
refinement.  The position of the boxes is with respect to a global
index space at that level.  For example, box 1 in the figure has {\tt
  lo} = (3,7) and {\tt hi} = (9,12).
